Setting up Data

### 2019-12-03 src/SetupData.Rmd
added the excluded mouse list, updating the setupdata results file

# First Steps

```{r MLH1.DF.setup, warning=FALSE}

@@

#Clean up main DF, MLH1_data
#remove duplicated data from MLH1 -- remove 1 or the two rows
#https://www.datanovia.com/en/lessons/identify-and-remove-duplicate-data-in-r/
#use distinct() in dlpyr()
MLH1_data <- MLH1_data %>% distinct(Original.Name, .keep_all = TRUE)#5216 to 4983

@@

MLH1_data <- add_mouse(MLH1_data)
MLH1_data <- add_category(MLH1_data)
MLH1_data <- add_strain(MLH1_data)
MLH1_data <- add_sex(MLH1_data)
MLH1_data <- add_subsp(MLH1_data)
#add species
MLH1_data <- add_species(MLH1_data)

#add a column with male adjusted MLH1 values (+1 to all males)
MLH1_data$adj_nMLH1.foci <- ifelse(MLH1_data$sex=="male", MLH1_data$nMLH1.foci+1, MLH1_data$nMLH1.foci)
MLH1_data$adj_nMLH1.foci <- as.numeric(MLH1_data$adj_nMLH1.foci)

#reorder dataframe
MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(Original.Name = factor(Original.Name) )

@@

@@

```{r kable.table}
#table comparing number of images in quantification batches
#ToDo:  correct the case of all batches, better names
#set an order to batches?
original_batches <- as.data.frame(table(original_DF$Batch) ) #these look bad
colnames(original_batches) <- c("BatchNum", "orginal")

batch.stats <- merge(original_batches,final_batches, by="BatchNum")## mm is the table of batch stats
```

`r kable(final_batches, caption = "This is the table caption") ) %>% kable_styling()`

@@

```{r mouse.table, echo=FALSE}
#source("~./MLH1repo/src/CommonFunc_MLH1repo.R")

@@

X number of mice are in the main DF (discribe the results for missing mice)

@@

```{r Age.Hists, echo=FALSE, warning=FALSE}

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_11.12.19.RData")

>>>>

```{r MLH1.DF.setup, warning=FALSE, echo=FALSE}

@@

```{r clean_MLH1_data, echo=FALSE}
#Clean up main DF, MLH1_data
#remove duplicated data from MLH1 -- remove 1 or the two rows
#https://www.datanovia.com/en/lessons/identify-and-remove-duplicate-data-in-r/
#use distinct() in dlpyr()
MLH1_data <- MLH1_data %>% distinct(Original.Name, .keep_all = TRUE)#5216 to 4983

@@

MLH1_data <- add_mouse(MLH1_data)
MLH1_data <- add_category(MLH1_data)
MLH1_data <- add_strain(MLH1_data)
MLH1_data <- add_sex(MLH1_data)
MLH1_data <- add_subsp(MLH1_data)
#add species
MLH1_data <- add_species(MLH1_data)
```

```{r exclude.mice, echo=FALSE}
#remove mice 
exclude_mice_list = c("18nov17_WSB_f1", "8oct14_WSB_f1", "8oct14_WSB_f3",
                      "10mar15_WSB_m2",
                      "8jun15_G_f3", "8jun15_G_f4",
                      "4jan17_LEW_f2",
                      "1apr15_PWD_f2", "8oct14_PWD_f5", "8oct14_PWD_f3", 
                      "12sep16_MSM_f3",
                      "27oct18_MOLF_m3",
                   "26oct18_SKIVE_f1","26oct18_SKIVE_f2","26oct18_SKIVE_f3",
                      "27aug18_CZECH_m1", "8jun18_CZECH_m1",
                      "3sep18_AST_m1","3sep18_TOM_m1","31jul17_HMI_m1",
                      "21aug17_SPI_f1", "30may18_SPIC_f1","8jun18_SPIC_m2")

MLH1_data <- MLH1_data[ ! MLH1_data$mouse %in% exclude_mice_list, ]

```{r adj_nMLH1, echo=FALSE}

#add a column with male adjusted MLH1 values (+1 to all males)
MLH1_data$adj_nMLH1.foci <- ifelse(MLH1_data$sex=="male", MLH1_data$nMLH1.foci+1, MLH1_data$nMLH1.foci)
MLH1_data$adj_nMLH1.foci <- as.numeric(MLH1_data$adj_nMLH1.foci)
```

```{r reorder.DF, echo=FALSE}
#reorder dataframe
MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(Original.Name = factor(Original.Name) )

@@

```{r kable.table, echo=FALSE}
#table comparing number of images in quantification batches
#ToDo:  correct the case of all batches, better names
#set an order to batches?
original_batches <- as.data.frame(table(original_DF$Batch) ) #these look bad
colnames(original_batches) <- c("BatchNum", "orginal")

batch.stats <- merge(original_batches,final_batches, by="BatchNum")## mm is the table of batch stats

`r kable(final_batches, caption = "Number of Images across all the anonimized Batches") %>% kable_styling()`

# Quality Cleaning steps

@@

Take out mice from the exclude list based on the output from Mouse level quality plots.

@@

Make mouse level tables

```{r mouse.table, echo=FALSE, warning=FALSE}

@@

 number of mice are in the main DF (discribe the results for missing mice)

@@

```{r Age.Hists, echo=FALSE, warning=FALSE, eval=FALSE}
#age.weeks col is missing

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_12.3.19.RData")
